\documentclass{article}
\begin{document}
\title{A DETAILED ONLINE HOTEL MANAGEMENT SYSTEM IN KAMALA AND SURROUNDING DISTRICTS}

\author{KAJJOBA MUDASILUl}
\maketitle
\paragraph{1.0 Introduction to an increasing creation of hotels in our country. As a result, the techniques of
management of modern hotels must adapt to changing circumstances. This system will help
to simplify the booking process while saving time and money, so that hotel managers could focus on what matters most: improving the guests’ experience
1.1. Background to the problem.
Hotel operators usually find it a demanding experience to operate hotel business and they usually find themselves on their feet. The question is why spend so much time on tedious tasks such as training employees and manually calculating monthly sales. Worst of all, do they have to be present at the front desk all the time to ensure everything was running smoothly? The answer is a No
Hotel Studio was coded by a Team of experienced Lasahara Systems software developers to meet the existent gap in electronic data management within the hospitality industry. However their software has limited features like user friendliness, secure login and easy backup. Since our local systems lack the full package of needed deliverables there is a need to address this issue and adapt what other systems like hotel executive have. Hotel Executive is packed full of features to increase occupancy rates, generate more revenue and make every part of your hotel run smoothly - from reservations to reception, back office to housekeeping, restaurant and bar.
1.2. Problem Statement The problem this project will address is to improve hotel management experience. Using convention methods such as pen and paper, spreadsheet, or offline software, you are more prone to issues that will consume your time and money. Using a hotel management system is like having an employee by your side to manage, organize, and secure your hotel information, but at a fraction of the price. Arka Uganda has designed systems that help in hotel management from booking and reservation, in-room entertainment, accountability, operations management; hotel services to daily reports of all the activities happening in a hotel but with almost one or two companies in business it is so expensive to acquire such systems therefore there is a need to curb the expenses for hotel managers and operators needing another hotel management system. 
The hotel operator and user should therefore expect an easy-to-use system for dealing with enquiries, bookings, guest information, tasks and billing
1.3. Aim and Objectives
1.3.1. General objective To simplify the booking process while saving time and money
To enable business owners to manage their businesses with ease and simplicity
1.3.2. Specific Objectives To automatically update a customer’s details
To provide secure online backup
To provide remote online access
To enable basic invoicing feature
1.4. Research Scope
The research scope is limited to hotels in major towns in Uganda because there is a need to address the existing gap in the management of electronic data in the hospitality industry
1.5. Research Significance
This study is important since it helps hotel owners to manage their hotels with a lot of ease and simplicity by providing a platform for training the employees at half the price
This study is also important because it improves customer experiences by providing them with important updates on the latest versions of release of the software
References
I have looked at existing systems like; hotel serena, Arka Uganda and hotel executive in the United Kingdom
Adapted from new vision
}
\end{document}
